Domain-Independent Detection of Emergency Situations\\Based on Social Activity Related to Geolocations

### 2018-02-22 paper_OLD.tex
add barbara's review as introduction to some sections and sort experiments and results

In this paper we have presented a methodology for detecting an emergency situation based on location for a specific country. This approach is independent of the textual features and can be used in different types of events and languages. We show that the users act as self-organized in the affected locations like citizen sensors when an emergency situation occurs. We furthermore have presented an analysis of geographic spread for different types of events that can be categorized. However, our experiment considers just a small portion of emergency situations, which is not representive for all types of crisis situations according to either the hazard type (natural or human-induced), temporal development (instantaneous or progressive) or geographic spread (diffused or focalized).

>>>>

In this paper we have presented a methodology for detecting an emergency situation based on location for a specific country. This approach is independent of the textual features and can be used in different types of events and languages. We show that the users act as self-organized in the affected locations like citizen sensors when an emergency situation occurs. We furthermore have presented an analysis of geographic spread for different types of events that can be categorized. However, our experiment considers just a small portion of emergency situations, which is not representative for all types of crisis situations according to either the hazard type (natural or human-induced), temporal development (instantaneous or progressive) or geographic spread (diffused or focalized).
